Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-22 manuscript/HIAs.qmd
indicator mean and sd per HIA

mu <- seq(0, 1, length.out=1000)
# Intersect nature3 with the HIA
temp <- nature3 |>
  st_intersection(infraMuni3) |>
  pivot_longer(cols = c(
    i_ADSV,
    i_alien,
    i_ditch),
    names_to = "indicator",
    values_to = "indicatorValue") |>
  filter(!is.na(indicatorValue)) |>
  group_by(indicator, Municipality, infrastructureIndex) |>
  summarise(mean )
```

>>>>

# Intersect nature3 with the HIA
stats_tbl <- nature3 |>
  st_intersection(infraMuni3) |>
  pivot_longer(cols = c(
    i_ADSV,
    i_alien,
    i_ditch),
    names_to = "indicator",
    values_to = "indicatorValue") |>
  filter(!is.na(indicatorValue)) |>
  mutate(area = drop_units(area)) |>
  group_by(indicator, Municipality, infrastructureIndex) |>
  summarise(sd = wgt_mean(indicatorValue,
      weights = area,
      sigma.x = case_when(
        indicator == "i_alien" ~ national_sd_alien,
        indicator == "i_ditch" ~ national_sd_ditch,
        indicator == "i_ADSV" ~ national_sd_ADSV,
        .default = NULL
      ),
      stat = "sd"),
    mean = wgt_mean(indicatorValue,
      weights = area,
      sigma.x = case_when(
        indicator == "i_alien" ~ national_sd_alien,
        indicator == "i_ditch" ~ national_sd_ditch,
        indicator == "i_ADSV" ~ national_sd_ADSV,
        .default = NULL
      ),
      stat = "mean"),
    n = n())
stats_tbl
```

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
```
